gtsummary

### 2020-12-10 rmarkdown-gtsummary.Rmd
updates

```{r}
tibble::tribble(
  ~Argument,       ~Description,
  "`label=`",       "specify the variable labels printed in table",
  "`type=`",        "specify the variable type (e.g. continuous, categorical, etc.)",
  "`statistic=`",   "change the summary statistics presented",
  "`digits=`",      "number of digits the summary statistics will be rounded to",
  "`missing=`",     "whether to display a row with the number of missing observations",
  "`missing_text=`","text label for the missing number row",
  "`sort=`",        "change the sorting of categorical levels by frequency",
  "`percent=`",     "print column, row, or cell percentages"
) %>%
  gt() %>%
  fmt_markdown(everything()) %>%
  as_latex() %>%
  as.character() %>%
  str_replace(fixed("\\toprule"), fixed("\\caption{\\label{tab:}\\texttt{tbl\\_summary()} function arguments}\\\\\n\\toprule")) %>%
  readr::write_lines("tbl_tbl_summary_args.tex")

@@

tbl_survfit_1 <-
  survfit(Surv(ttdeath, death) ~ trt, trial) %>%
  tbl_survfit(times = c(12, 24),
              label_header = "**{time} Month**") %>%
  add_p()
```

>>>>

```{r}
tibble::tribble(
  ~Argument,       ~Description,
  "`label=`",       "specify the variable labels printed in table",
  "`type=`",        "specify the variable type (e.g. continuous, categorical, etc.)",
  "`statistic=`",   "change the summary statistics presented",
  "`digits=`",      "number of digits the summary statistics will be rounded to",
  "`missing=`",     "whether to display a row with the number of missing observations",
  "`missing_text=`","text label for the missing number row",
  "`sort=`",        "change the sorting of categorical levels by frequency",
  "`percent=`",     "print column, row, or cell percentages",
  "`include=`",     "list of variables to include in summary table"
) %>%
  gt() %>%
  fmt_markdown(everything()) %>%
  as_latex() %>%
  as.character() %>%
  str_replace(fixed("\\toprule"), fixed("\\caption{\\label{tab:}\\texttt{tbl\\_summary()} function arguments}\\\\\n\\toprule")) %>%
  readr::write_lines("tbl_tbl_summary_args.tex")

@@

tbl_survfit_1 <-
  list(survfit(Surv(ttdeath, death) ~ trt, trial),
       survfit(Surv(ttdeath, death) ~ grade, trial)) %>%
  tbl_survfit(times = c(12, 24),
              label_header = "**{time} Month**") %>%
  add_p()
```
